MCC Models

### 2020-09-22 papers/full_paper/models.Rmd
clean repo
update model algo

@@

var steps = 5000
var samples = 1
var mll = AIS(model, {steps:steps, samples: samples})
mll

@@

```{r}
# child_ex3_pragm_model_likelihood<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   chains = 3,
#   cores = 3
# )%>%
#   saveRDS("../../stats/saves/child_ex3_pragm_model_loglike.rds")

@@

var steps = 5000
var samples = 1
var mll = AIS(model, {steps:steps, samples: samples})
mll
'
```

```{r}
# child_ex3_pragm_model_noise_likelihood<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.noise.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   chains = 3,
#   cores = 3
# )%>%
#   saveRDS("../../stats/saves/child_ex3_pragm_model_noise_loglike.rds")

@@

var steps = 5000
var samples = 1
var mll = AIS(model, {steps:steps, samples: samples})
mll
'
```

```{r}
# child_ex3_pragm_model_developmental_noise_likelihood<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.developmental.noise.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   chains = 3,
#   cores = 3
# )%>%
#   saveRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")

@@

var steps = 5000
var samples = 1
var mll = AIS(model, {steps:steps, samples: samples})
mll
'
```

```{r}
# child_ex3_flat_prior_model_likelihood<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   chains = 3,
#   cores = 3
# )%>%
#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_loglike.rds")

@@

var steps = 5000
var samples = 1
var mll = AIS(model, {steps:steps, samples: samples})
mll
'
```

```{r}
# child_ex3_flat_prior_model_noise_likelihood<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.noise.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   chains = 3,
#   cores = 3
# )%>%
#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_noise_loglike.rds")

@@

var steps = 5000
var samples = 1
var mll = AIS(model, {steps:steps, samples: samples})
mll
'
```

```{r}
# child_ex3_flat_prior_model_developmental_noise_likelihood<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.developmental.noise.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   chains = 3,
#   cores = 3
# )%>%
#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise_loglike.rds")

@@

var steps = 5000
var samples = 1
var mll = AIS(model, {steps:steps, samples: samples})
mll
'
```

```{r}
# child_ex3_prior_only_model_likelihood<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   chains = 3,
#   cores = 3
# )%>%
#   saveRDS("../../stats/saves/child_ex3_prior_only_model_loglike.rds")

@@

var steps = 5000
var samples = 1
var mll = AIS(model, {steps:steps, samples: samples})
mll
'
```

```{r}
# child_ex3_prior_only_model_noise_likelihood<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   chains = 3,
#   cores = 3
# )%>%
#   saveRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")

@@

var steps = 5000
var samples = 1
var mll = AIS(model, {steps:steps, samples: samples})
mll
'
```

```{r}
# child_ex3_prior_only_model_developmental_noise_likelihood<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.developmental.noise.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   chains = 3,
#   cores = 3
# )%>%
#   saveRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise_loglike.rds")

>>>>

```{r}
child_ex3_pragm_model_likelihood<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  chains = 3,
  cores = 3
)%>%
  saveRDS("../../stats/saves/child_ex3_pragm_model_loglike.rds")

child_ex3_pragm_model_noise_likelihood<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.noise.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  chains = 3,
  cores = 3
)%>%
  saveRDS("../../stats/saves/child_ex3_pragm_model_noise_loglike.rds")

child_ex3_pragm_model_developmental_noise_likelihood<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.developmental.noise.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  chains = 3,
  cores = 3
)%>%
  saveRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")

child_ex3_flat_prior_model_likelihood<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  chains = 3,
  cores = 3
)%>%
  saveRDS("../../stats/saves/child_ex3_flat_prior_model_loglike.rds")

child_ex3_flat_prior_model_noise_likelihood<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.noise.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  chains = 3,
  cores = 3
)%>%
  saveRDS("../../stats/saves/child_ex3_flat_prior_model_noise_loglike.rds")

child_ex3_flat_prior_model_developmental_noise_likelihood<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.developmental.noise.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  chains = 3,
  cores = 3
)%>%
  saveRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise_loglike.rds")

child_ex3_prior_only_model_likelihood<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  chains = 3,
  cores = 3
)%>%
  saveRDS("../../stats/saves/child_ex3_prior_only_model_loglike.rds")

child_ex3_prior_only_model_noise_likelihood<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  chains = 3,
  cores = 3
)%>%
  saveRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")

child_ex3_prior_only_model_developmental_noise_likelihood<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.developmental.noise.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  chains = 3,
  cores = 3
)%>%
  saveRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise_loglike.rds")

@@

var steps = 5000
var samples = 100
var mll = AIS(model, {steps:steps, samples: samples})
mll

@@

```{r}
child_ex3_pragm_model_likelihood<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  chains = 3,
  cores = 3
)%>%
  saveRDS("../../stats/saves/child_ex3_pragm_model_loglike.rds")

@@

var steps = 5000
var samples = 100
var mll = AIS(model, {steps:steps, samples: samples})
mll
'
```

```{r}
child_ex3_pragm_model_noise_likelihood<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.noise.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  chains = 3,
  cores = 3
)%>%
  saveRDS("../../stats/saves/child_ex3_pragm_model_noise_loglike.rds")

@@

var steps = 5000
var samples = 100
var mll = AIS(model, {steps:steps, samples: samples})
mll
'
```

```{r}
child_ex3_pragm_model_developmental_noise_likelihood<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.developmental.noise.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  chains = 3,
  cores = 3
)%>%
  saveRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")

@@

var steps = 5000
var samples = 100
var mll = AIS(model, {steps:steps, samples: samples})
mll
'
```

```{r}
child_ex3_flat_prior_model_likelihood<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  chains = 3,
  cores = 3
)%>%
  saveRDS("../../stats/saves/child_ex3_flat_prior_model_loglike.rds")

@@

var steps = 5000
var samples = 100
var mll = AIS(model, {steps:steps, samples: samples})
mll
'
```

```{r}
child_ex3_flat_prior_model_noise_likelihood<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.noise.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  chains = 3,
  cores = 3
)%>%
  saveRDS("../../stats/saves/child_ex3_flat_prior_model_noise_loglike.rds")

@@

var steps = 5000
var samples = 100
var mll = AIS(model, {steps:steps, samples: samples})
mll
'
```

```{r}
child_ex3_flat_prior_model_developmental_noise_likelihood<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.developmental.noise.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  chains = 3,
  cores = 3
)%>%
  saveRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise_loglike.rds")

@@

var steps = 5000
var samples = 100
var mll = AIS(model, {steps:steps, samples: samples})
mll
'
```

```{r}
child_ex3_prior_only_model_likelihood<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  chains = 3,
  cores = 3
)%>%
  saveRDS("../../stats/saves/child_ex3_prior_only_model_loglike.rds")

@@

var steps = 5000
var samples = 100
var mll = AIS(model, {steps:steps, samples: samples})
mll
'
```

```{r}
child_ex3_prior_only_model_noise_likelihood<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  chains = 3,
  cores = 3
)%>%
  saveRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")

@@

var steps = 5000
var samples = 100
var mll = AIS(model, {steps:steps, samples: samples})
mll
'
```

```{r}
child_ex3_prior_only_model_developmental_noise_likelihood<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.developmental.noise.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  chains = 3,
  cores = 3
)%>%
  saveRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise_loglike.rds")
